Automating the Ontological Argument

### 2015-12-11 Papers/InProgress/IJCAI/paper.tex
added graphics

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle. Easy to understand in 
in KB and KT, slightly harder in K.

>>>>

\subsection{Argument Reconstruction in Isabelle}
Present the argument informal and in Isabelle (see
Fig.~\ref{InconsistencyIsabelleK}). Easy to understand in 
in KB and KT, slightly harder in K.
\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/InconsistencyIsabelleK.png}}
\caption{Reconstruction of inconsistency in Isabelle/HOl..} \label{InconsistencyIsabelleK}
\end{figure*}
